---
title: "Sample output of alignment.stat"
author: "Paul Rognon"
date: "18/11/2019"
output: html_document
params:
  sequence1: gi32141095_N_1.fa
  sequence2: gi32141095_N_0.fa
  path: ~/MESIO/Bioinformatica/Task 1&2
  type: "DNA"
  alignment: "local"
  matrix: "BLOSUM50"
  opening_penal: -5
  ext_penal: -1
  times_shuffling: 1000
  seq_shuffled: 1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```

### Summary of inputs:
 * sequence 1: `r params$sequence1`
 * sequence 2: `r params$sequence2`
 * sequence type: `r params$type`
 * alignment type: `r params$alignment`
 * substitution matrix: `r params$matrix`
 * gap opening penalty: `r params$opening_penal`
 * gap extension penalty: `r params$ext_penal`
 * number of shuffling times: `r params$times_shuffling`
 * shuffled sequence: `r params$seq_shuffled`
 
### Results
The output is composed of: a summary of the scores distribution obtained by shuffling, the parameters of the Gumbel distribution, the alignment score, standardized score and p-value.

```{r}
path=params$path
  
as<-alignment.stat(
  sequence1=paste(path,params$sequence1,sep="/"),
  sequence2=paste(path,params$sequence2,sep="/"),
  type_seq=params$type,
  alignment=params$alignment,
  submatrix=params$matrix,
  gapOpenPenal=params$opening_penal,
  gapExtPenal=params$ext_penal,
  N=params$times_shuffling,
  shuffled=params$seq_shuffled)
```

